---
title: "p8105_hw5_jh4324"
author: "Jiying Han"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(stats)
library(purrr)

knitr::opts_chunk$set(
	fig.width = 6, 
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d



```

This is my solution for HW5

## Problem 1

read in the data
```{r}
homicide_df = 
  read.csv("./data/homicide-data.csv") %>%
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest"~"unsolved",
      disposition == "Open/No arrest"~"unsolved",
      disposition == "Closed by arrest"~"solved"
    )
   ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") 

```

let's look at this a bit

```{r}
aggregate_df = 
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )
```

can i do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
 broom::tidy() 
```

try to iterate...

```{r}
result_df = 
  aggregate_df %>% 
   mutate(
     prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n =.y)),
     tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))
   ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

make a plot

```{r}
result_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90,vjust = 0.5, hjust = 1))
```


## Problem 2


Import one dataset
```{r  message = FALSE}
path_df =
  tibble(
  path = list.files("./data/data2")
) %>% 
  mutate(path = str_c("./data/data2/", path),
         observations = map(.x = path, ~read_csv(.x))
         ) %>% 
  separate(path,c("subject_id","format"),sep = ".csv" ) %>% 
  separate(subject_id,c("format","subject_id"),sep = "2/" ) %>% 
  select(-format) %>% 
  separate(subject_id,c("arm","subject_id"),sep = "_") %>% 
  mutate(
  arm = case_when(
      arm == "con"~"control",
      arm == "exp"~"experiment"
    )) %>% 
  unnest(observations) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    values_to ="observations"
  ) %>% 
  mutate(
    week = str_replace(week,"week_",""),
    week = as.factor(week)) 

```


Make a spaghetti plot
```{r error = TRUE}
spaghetti_plot = 
  path_df %>%
  ggplot(aes(x = week, y = observations, group = arm, color = arm)) + 
  geom_path() +
  labs(
    title = "Observations of control group and experimental group",
    x = "Week",
    y = "Observation"
  )

ggsave("spaghetti_plot.jpg")

spaghetti_plot
```

Comment: In these eight weeks, we can finds that in experimental groups, the overall  observational values are higher than the control groups. And the trend of the experimental groups is increasing. As for the control groups, the trend is approximately fluctuate without apparent increasing or decreasing.

## Problem 3 (simulation - ttest -  estimate - pvalue - plot/summarize of pvalue and estiamte by significant different or not)

Generate dataset

```{r}
set.seed(1000)

nd_ttest = function(mu){
  norm_df = 
    tibble(x = rnorm(mean = mu, n =30, sd = 5)) 
  
  norm_df %>% 
    summarize(
      t.test(x, mean = 0,conf.level = 0.95) %>% 
      broom::tidy() %>%
      select(estimate,p.value)
                         )
   
}
nd_ttest(0)

 
set.seed(1000)
sample_df = function(mu){
  rerun(5000,map(.x = mu, ~nd_ttest(.x))) %>% 
  bind_rows()
}

sample_df(0)
```


Repeat the above

```{r}
set.seed(10000)
mu_df = 
  tibble(
    mu = c(0,1,2,3,4,5,6)
      ) %>% 
  mutate(
    output_lists = map(.x = mu, ~sample_df(.x))
  )

```


Summarize 

```{r}
set.seed(10000)
mureject_df = 
  mu_df %>% 
  unnest(output_lists) %>% 
  mutate(mu = as.numeric(mu)) %>% 
  group_by(mu) %>% 
  mutate(
    reject = case_when(
      p.value >= 0.05~ 0,
      p.value < 0.05~ 1
    )
  )  %>% 
  mutate(
    mu = as.factor(mu),
    reject = as.numeric(reject)) %>% 
  select(mu,reject) %>% 
  summarize(
    test_total = n(),
    reject_total = sum(reject == "1" ),
    proportion = reject_total/test_total
  )
    

```


Plot - proportion of time the null was rejected

```{r}
set.seed(1000)
mureject_df %>% 
  mutate(mu = as.numeric(mu)-1) %>% 
  ggplot(aes( x = mu , y = proportion, color = mu)) + 
  geom_point() +
  geom_line() +
  labs(
    title = "Association between effect size and power",
    x = "True μ",
    y = "Proportion of times the null was rejected (Power)"
  )
  
```

Describe the association between effect size and power.
With the effect size increasing, the proportion of times the null was rejected rapidly increasing, then after the true μ = 4, it becomes steady. And it reaches 1 when true μ = 5.


Plot - Average estimate of μ hat and true value of μ

```{r}
 mu_df %>% 
  unnest(output_lists) %>% 
  mutate(mu = as.numeric(mu)) %>% 
  group_by(mu) %>% 
  summarize(
    average_estimate = mean(estimate)
  ) %>% 
  ggplot(aes(x = mu, y = average_estimate, color = mu)) +
  geom_point() +
  geom_line() +
  labs(
    title = "Average estimate of μ hat and true value of μ",
    x = "True value of μ",
    y = "Average estimate of μ hat "
   )
```


Plot - Average estimate of μ hat only in samples for which the null was rejected and true value of μ 
```{r}
mu_df %>% 
  unnest(output_lists) %>% 
  mutate(
    mu = as.numeric(mu),
    reject = case_when(
      p.value >= 0.05 ~1,
      p.value < 0.05~ 0
    )
  ) %>% 
  filter(reject == 0) %>% 
  group_by(mu) %>% 
  summarize(
    average_estimate = mean(estimate)
   ) %>% 
  ggplot(aes( x = mu, y = average_estimate, color =mu )) +
  geom_point() +
  geom_line() +
  labs(
    title = "Average estimate of μ hat only in samples for which the null was rejected and true value of μ ",
    x = "True value of μ",
    y = "Average estimate of μ hat"
  )
```



The average estimate of μ hat equal to true μ. But as for average estimate of μ hat only in samples for which the null was rejected, it only equals to true mu when mu = 4-6. When true mu = 0-3, especially when mu close to 0, the number of samples for which the null was rejected becomes less(draw from the first plot), and within these samples, the estimate of mu hat is away from true mu, thus it isn't equal to the true mu. For true mu approach to 6, more and more samples are rejected, and most estimate of mu hat far away from true mu, therefore, the average estimate of mu hat in samples for which the null was rejected is much closer to true mu and even equal to true mu.
